Multiphyscis modeling for the Fluoride-salt-cooled High-temperature Reactor (FHR)

### 2018-07-23 paper/main.tex
Updates from ShareLaTeX

As shown in Figure \ref{fig:model_geom}, the multi-physics reactor core model is composed by three regions: an upper porous region that represents a fuel pebble and flibe salt porous mixture, a lower region with only flibe salt and an outer graphite reflector region. Coupled heat transfer and neutron diffusion equations are solved with homogenized material properties for each region.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.2\textwidth}
    \includegraphics[width = \columnwidth]{./images/diffusion/tmsr/2d_schematic.png}
    %\caption{Schematic of the TMSR core model geometry}
  \end{subfigure}
  ~
  \begin{subfigure}{0.55\textwidth}
    \includegraphics[width = \columnwidth]{./images/diffusion/tmsr/finer.png}
    %\caption{Schematic of the 2D mesh}
  \end{subfigure}
  \caption{Schematic of the multi-physics model for TMSR SF-1 and a three-dimensional mesh}
  \label{fig:model_geom}
\end{figure}

@@

\subsection{Steady state results}
After careful code-to-code verification for the multi-physics model, parameters such as power, flibe and fuel temperatures, and neutron flux are computed. Uniform temperature and uniform upward velocity are imposed as the inlet boundary condition. Vacuum boundary condition for neutron diffusion is used outside of the reflector.

@@

\section{Conclusion}
Strict safety requirement for next-generation reactors along with the progress in computer technology prompts the development, qualification and application of time-dependent multiphysics models for nuclear reactors.
In this paper has developed a methodology for building coupled neutronics/thermal-hydraulics model for FHRs based on multi-group neutron diffusion and porous media CFD, with a multi-scale treatment. The model provides high resolution two dimensional or three dimensional results within a reasonable amount of time on a computer with 16.0 GB RAM and four Intel Core equipped with i7-4790K CPU at 4.00 GHz.

>>>>

As shown in Figure \ref{fig:model_geom}, the multiphysics reactor core model is composed by three regions: an upper porous region that represents a fuel pebble and flibe salt porous mixture, a lower region with only flibe salt and an outer graphite reflector region. Coupled heat transfer and neutron diffusion equations are solved with homogenized material properties for each region.

\begin{figure}[h]
  \centering
  \begin{subfigure}{0.2\textwidth}
    \includegraphics[width = \columnwidth]{./images/diffusion/tmsr/2d_schematic.png}
    %\caption{Schematic of the TMSR core model geometry}
  \end{subfigure}
  ~
  \begin{subfigure}{0.55\textwidth}
    \includegraphics[width = \columnwidth]{./images/diffusion/tmsr/finer.png}
    %\caption{Schematic of the 2D mesh}
  \end{subfigure}
  \caption{Schematic of the multiphysics model for TMSR SF-1 and a three-dimensional mesh}
  \label{fig:model_geom}
\end{figure}

@@

\subsection{Steady state results}
After careful code-to-code verification for the multiphysics model, parameters such as power, flibe and fuel temperatures, and neutron flux are computed. Uniform temperature and uniform upward velocity are imposed as the inlet boundary condition. Vacuum boundary condition for neutron diffusion is used outside of the reflector.

@@

\section{Conclusion}
Strict safety requirement for next-generation reactors along with the progress in computer technology prompts the development, qualification and application of time-dependent multiphysics models for nuclear reactors.
In this paper has developed a methodology for building coupled neutronics/thermal-hydraulics model for FHRs based on multigroup neutron diffusion and porous media CFD, with a multiscale treatment. The model provides high resolution two dimensional or three dimensional results within a reasonable amount of time on a computer with 16.0 GB RAM and four Intel Core equipped with i7-4790K CPU at 4.00 GHz.
